### 2021-02-15 results.tex
Minor

Our first study performed a non-exact replication of Bao et al work.
Our study differs from the original because here we isolated the effect
of the DroidFax static analysis algorithms in the performance to
identify malicious apps using the test case generation tools for
mining sandboxes. In addition, we discarded six pairs of
Android apps we were not able to instrument---out of the $102$ pairs used in the \original work.
\rb{All of this following information should be detailed in
the study settings, and not repeated here if it is already there.} {\color{red}We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute. The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al. results.}

>>>>

Our first study performed a non-exact replication of Bao et al work.
\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }
Our study differs from the original because here we isolated the effect
of the DroidFax static analysis algorithms in the performance to
identify malicious apps using the test case generation tools for
mining sandboxes. In addition, we discarded six pairs of
Android apps we were not able to instrument---out of the $102$ pairs used in the \original work.
\rb{All of this following information should be detailed in
the study settings, and not repeated here if it is already there.} {\color{red}We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute. The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al. results.}
